% !TeX spellcheck = <none>

\input{preamble.tex}

\lfoot{
    \footnotesize \today \\
    En, \hyperref{https://github.com/SMR76/curriculum-vitae/raw/main/cv.fa.pdf}{}{}{Fa} \\
    \hyperref{https://github.com/SMR76/curriculum-vitae}{}{}{Source} \\
}

\begin{document}
    \lstset{
        frame=tb,
        basicstyle=\color{steelBlue}\linespread{0.8}\ttfamily,
        columns=fullflexible,
        keepspaces=false,
        tabsize=4,
        autogobble,
        breaklines=true,
        breakatwhitespace=true,
        stringstyle=\color{orange},
        commentstyle=\color{gray},
        keywordstyle=\color{purple},
        language=java,
        aboveskip=3mm,
        belowskip=3mm,
        showstringspaces=false,
        columns=flexible,
        captionpos=b,
        numbers=left,
        numbersep=5pt,
        numberstyle=\color{gray}\linespread{0.8}\ttfamily,
        postbreak=\mbox{\textcolor{blue}{$\hookrightarrow$}\space}
    }

    \hypersetup{urlcolor=blueLink}

    \newcounter{dateone}%
    \newcounter{datetwo}%
    \setmydatenumber{dateone}{1997}{11}{11}%
    \setmydatenumber{datetwo}{\the\year}{\the\month}{\the\day}%
    \FPeval\myage{trunc(div(sub(\thedatetwo,\thedateone),365.2425),0)}

    \noindent Hello, my name is Morteza Razavi.	\\
    I graduated from
    \hyperref{https://en.wikipedia.org/wiki/Quchan\_University\_of\_Advanced\_Technologies\_Engineering}{}{}{Quchan university of technology}.
        with a Bachelor's degree. \\
    I have programming expertise with Qt, C++, and QML. \\
    I enjoy art and UI design. \\
    \noindent\textcolor{gray}{\rule{\linewidth}{1pt}}
    I'm also informed on the following subjects: \vspace{5mm}

    \begin{itemize}[nosep]
        \item Git version control.
        \item GitHub CI/CD (just
            \hyperref{https://github.com/SMR76/github-action-test}{}{}{this} little GitHub workflow for Qt Windows build).
        \item GNU/Linux (my main OS is Windows, but I like to use Linux distributions too).
        \item Arduino programming.
        \item ARM programming (currently learning).
        \item \LaTeX.
        \item JavaScript and JQuery, as used in my \hyperref{https://github.com/SMR76/SMR76.github.io}{}{}{website}.
        \item And some knowledge of CSS and Bootstrap and PHP.
    \end{itemize}\vspace{5mm}
    \noindent\textcolor{gray}{\rule{\linewidth}{1pt}}
    \noindent Some of the projects which I developed:\vspace{5mm}
    \begin{itemize}[nosep]
        \item \hyperref{https://github.com/SMR76/knight-pen}{}{}{knight-pen}, Simple screen annotation software.
        \item \hyperref{https://github.com/SMR76/qml-neumorphism}{}{}{qml-neumorphism},
        QtQuick Neumorphism (soft UI) style for Qt applications.
        \item \hyperref{https://github.com/SMR76/qml-snow-white}{}{}{qml-snow-white}
        QtQuick Snow White style for Qt applications.
        \item \hyperref{https://github.com/SMR76/smr-wp-plugin}{}{}{smr-wp-plugin}, All in one WordPress plugin.
        \item \hyperref{https://github.com/SMR76/car-alarm}{}{}{car-alarm},
        This project is centered on building hardware that can be installed in your automobile to help safeguard it from thieves and give you more control over it.
    \end{itemize}\vspace{5mm}
    See my other projects on \hyperref{https://github.com/SMR76?tab=repositories}{}{}{GitHub}.\\
    Contact me:
    \begin{itemize}[nosep]
        \item \textcolor{gmail}{\faAt}\ Gmail: \hyperref{mailto:seyyed.morteza.razavi.76@gmail.com} {}{}{seyyed.morteza.razavi.76@gmail.com}
        \item \textcolor{telegram}{\faSendO}\ telegram: \hyperref{tg://resolve?domain=S\_M\_R0}{}{}{\faAt S\_M\_R0}
        \item \textcolor{edge}{\faEdge}\ my website: \hyperref{https://SMR76.github.io/#contactMe}{}{}{SMR76.github.io}
    \end{itemize}
\end{document}
