% !TeX spellcheck = en_US
\documentclass[a4paper,12pt]{report}

\usepackage{color}
\usepackage{xparse}
\usepackage{fourier}
\usepackage{amsmath}
\usepackage{dirtree}
\usepackage{verbatim}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{outlines}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage{fancyvrb}
\usepackage{listings}
\usepackage{multicol}
\usepackage{makecell}
\usepackage{setspace}
\usepackage{subcaption}
\usepackage{transparent}
\usepackage{indentfirst}
\usepackage{transparent}
\usepackage[usenames,dvipsnames,table]{xcolor}
\usepackage{datenumber,fp}
\usepackage{lstautogobble}
\usepackage[none]{hyphenat}
\usepackage[explicit]{titlesec}
\usepackage[breakable]{tcolorbox}
\usepackage[font=footnotesize]{caption}
\usepackage[colorlinks,linkcolor=blue,citecolor=red,urlcolor=gray]{hyperref}
\tcbuselibrary{breakable, skins}
\usepackage{fontspec}
\usepackage{fontawesome}

%% ------------ font settings -------------
%\fontspec[ Path = ./fonts/ ]{icofont.ttf}
%\newfontfamily\icofont{IcoFont}
\setmainfont{Consolas}

%% ----------- helper command -------------

\newcommand{\lrm}[1]{\textcolor{steelBlue}{\texttt{#1}}}

\newcommand{\qt}[1]{``#1''}

\definecolor{ao}				{rgb}{0.00, 0.50, 0.00}
\definecolor{codeGreen}			{rgb}{0.00, 0.70, 0.50}
\definecolor{lavendergray}		{rgb}{0.87, 0.86, 0.92}
\definecolor{mint}				{rgb}{0.24, 0.71, 0.54}
\definecolor{aliceblue}			{rgb}{0.94, 0.97, 1.00}
\definecolor{customCommentGreen}{rgb}{0.13, 0.65, 0.47}
\definecolor{steelBlue}			{rgb}{0.00, 0.00, 0.50}
\definecolor{blueLink}			{rgb}{0.10, 0.05, 0.67}
\definecolor{stringGreen}		{rgb}{0, 0.5, 0}

\definecolor{twitter}			{rgb}{0.11, 0.63, 0.95}
\definecolor{linkedin}			{rgb}{0.00, 0.47, 0.71}
\definecolor{telegram}			{rgb}{0.15, 0.62, 0.85}
\definecolor{gmail}				{rgb}{0.87, 0.33, 0.28}

\DeclareCaptionFormat{listing}{\vskip1pt#1#2#3}
\captionsetup[lstlisting]{format=listing,singlelinecheck=false, margin=0pt, font={sf},labelsep=space,labelfont ={sf}}
\renewcommand\lstlistingname{snippet code}

\setlength{\headheight}{12pt}

\fancypagestyle{plain}{%
	\fancyhf{}%
	\renewcommand{\headrulewidth}{0pt}%
	\lhead{{\small\color{gray} S.M.R }}
	\rhead{
		{\hypersetup{urlcolor=black}\hyperref{https://github.com/SMR76}{}{}{\faGithub}}
		{\hypersetup{urlcolor=twitter}\hyperref{https://twitter.com/S\_M\_R\_67}{}{}{\faTwitter}}
		{\hypersetup{urlcolor=linkedin}\hyperref{https://www.linkedin.com/in/seyyed-morteza-razavi-403b2a196/}{}{}{\faLinkedin}}
		{\hypersetup{urlcolor=Magenta}\hyperref{https://www.instagram.com/s\_m\_r76/}{}{}{\faInstagram}}
		{\hypersetup{urlcolor=telegram}\hyperref{tg://resolve?domain=S\_M\_R0}{}{}{\faSendO}}
		{\hypersetup{urlcolor=gmail}\hyperref{mailto:seyyedmortezarazavi76@gmail.com}{}{}{\faAt}}
	}
}

\pagestyle{plain}

\begin{document}
	\lstset{
		frame=tb,
		basicstyle=\color{steelBlue}\linespread{0.8}\ttfamily,
		columns=fullflexible,
		keepspaces=false,
		tabsize=4,
		autogobble,
		breaklines=true,
		breakatwhitespace=true,
		stringstyle=\color{orange},
		commentstyle=\color{gray},
		keywordstyle=\color{purple},
		language=java,
		aboveskip=3mm,
		belowskip=3mm,
		showstringspaces=false,
		columns=flexible,
		captionpos=b,
		numbers=left,
		numbersep=5pt,
		numberstyle=\color{gray}\linespread{0.8}\ttfamily,
		postbreak=\mbox{\textcolor{blue}{$\hookrightarrow$}\space}
	}

	\hypersetup{urlcolor=blueLink}

	\newcounter{dateone}%
	\newcounter{datetwo}%
	\setmydatenumber{dateone}{1997}{11}{11}%
	\setmydatenumber{datetwo}{\the\year}{\the\month}{\the\day}%
	\FPeval\myage{trunc(div(sub(\thedatetwo,\thedateone),365.2425),0)}

	\noindent Hi, my name is Seyyed Morteza Razavi.			\\
	I'm \myage\ years old.				\\
	I have a Bachelor's degree from
	\hyperref{https://fa.wikipedia.org/wiki/دانشگاه\_صنعتی\_قوچان}{}{}{Quchan university of technology}.						\\
	I have experience with Qt, C++, and QML programming.	\\
	I love painting and UI designing.						\\
	\noindent\textcolor{gray}{\rule{\linewidth}{1pt}}
	I'm also familiar with the following topics:			\vspace{5mm}

	\begin{itemize}[nosep]
		\item Git version control.
		\item GitHub CI/CD (just
			\hyperref{https://github.com/SMR76/github-action-test}{}{}{this} little GitHub workflow for Qt Windows build).
		\item Linux (my main OS is Windows, but I like to use Linux distributions too).
		\item \LaTeX.
		\item JavaScript and JQuery, as used in my \hyperref{https://github.com/SMR76/SMR76.github.io}{}{}{website}.
		\item And a little experience in CSS and Bootstrap.
		\item Arduino programming.
		\item ARM programming (currently learning).
	\end{itemize}\vspace{5mm}
	\noindent\textcolor{gray}{\rule{\linewidth}{1pt}}
	\noindent Some of the projects which I developed:\vspace{5mm}
	\begin{itemize}[nosep]
		\item \hyperref{https://github.com/SMR76/qml-neumorphism}{}{}{qml-neumorphism},
		QtQuick Neumorphism (soft UI) style for Qt applications.
		\item \hyperref{https://github.com/SMR76/smr-wp-plugin}{}{}{smr-wp-plugin}, all in one WordPress plugin.
		\item \hyperref{https://github.com/SMR76/car-alarm}{}{}{car-alarm},
		this project is based on designing hardware that installs in your car and helps to protect the vehicle against thieves and have better control over it.
		\item \hyperref{https://github.com/SMR76/adobe-connect-offline-player}{}{}{adobe-connect-offline-player},
				a video player which plays adobe connect record packages.
		\item \hyperref{https://github.com/SMR76/persian-subtitle-fixer}{}{}{persian-subtitle-fixer}.
	\end{itemize}\vspace{5mm}
	See my other projects on \hyperref{https://github.com/SMR76?tab=repositories}{}{}{GitHub}.\\
	Contact me:
	\begin{itemize}[nosep]
		\item \textcolor{gmail}{\faAt}\ Gmail: \hyperref{mailto:seyyedmortezarazavi76@gmail.com} {}{}{seyyedmortezarazavi76@gmail.com}
		\item \textcolor{telegram}{\faSendO}\ telegram: \hyperref{tg://resolve?domain=S\_M\_R0}{}{}{\faAt S\_M\_R0}
		\item \textcolor{black}{\faGithub}\ my website: \hyperref{https://SMR76.github.io/#contactMe}{}{}{SMR76.github.io}
	\end{itemize}
\end{document}
